---
author: |
  | University of Washington
  | School of Aquatic and Fishery Sciences
  | Seafood Globalization Lab
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
header-includes:
  - \usepackage{placeins}
params: 
  countries_i: NULL
  country_i_dwf: NULL
  country_i_consump: NULL
  country_i_eez_fishing: NULL
  foc_logic: NULL
---

```{r setup, include=FALSE, cache=FALSE}

# set global code chunk options
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      #fig.fullwidth = TRUE,
                       fig.width = 6,
                       fig.asp = 0.618,
                      #eval.after = "fig.cap", # eval code first then options
                      cache = TRUE)

# load packages
library(rmarkdown)
library(knitr) # Need package version 1.44 or up for quarto
library(countrycode) # convert and standardize country id
library(magrittr) # pipe function
library(ggplot2) # visualization
library(forcats) #reorder factors
library(stringr)
library(purrr) # iteration 
library(scales) # adjust display of plot numbers
library(cowplot) # arange plots together
# install old version of exploreARTIS
#install_github("Seafood-Globalization-Lab/exploreARTIS@c0f34b90172f716068c9b98df5ed491ca5085162")
# install AM updates branch, force new install, and do not update global enviro package versions
# install_github("Seafood-Globalization-Lab/exploreARTIS@AM-updates",
#                upgrade = "never", 
#                force = TRUE)
library(exploreARTIS) # custom ARTIS viz package 
library(shadowtext) # custom labeling on horizontal bar figures
library(egg) # arrange plots

# pull parameters into objects
country_iso3c <- params$countries_i
country_i_dwf <- params$country_i_dwf
country_i_consump <- params$country_i_consump
country_i_eez_fishing <- params$country_i_eez_fishing
foc_logic <- params$foc_logic

# iso3c to country name
country_name <- countrycode(country_iso3c,
                            origin = "iso3c",
                            destination = "country.name")

# read in annotations script
knitr::read_chunk(file.path(anndir, 
                            glue::glue({country_iso3c},".R")))

# knitr hook to prevent figure floating -- restricts fig.fullwidth=T option
knitr::knit_hooks$set(plot = function(x, options)  {
  paste0(knitr::hook_plot_tex(x, options), "\n\\FloatBarrier\n")
})

# selectively apply hook to non fullwidth figures in code chunks
# knitr::knit_hooks$set(plot = function(x, options) {
#   if (isTRUE(options$fig.fullwidth)) {
#     knitr::hook_plot_tex(x, options)
#   } else {
#     paste0(knitr::hook_plot_tex(x, options), "\n\\FloatBarrier\n")
#   }
# })


```

---
title: |
  | Oceana Distant Water Fishing Report: 
  | `r country_name`
---

# Overview

This report provides an analysis of distant water fishing (DWF) related to `r country_name`. We define distant water fishing as capture fishery landings that occur in the exclusive economic zone (EEZ) of a country other than the flag of the country. 

There are three aspects of distant water fishing investigated in this report:

1) DWF activities by other nations within the focal country's EEZ
2) The focal country's own DWF activities
3) The focal country's consumption of aquatic foods sourced via DWF (conducted by them or another country)

```{r, eval = foc_logic == TRUE, results='asis'}
cat(paste0("**Please note**: ", country_name, " been declared a flag of convience (FOC) by the International Transport Workers Federation's (ITF) Fair Practices Committee (a joint committee of ITF seafarers' and dockers' unions), which runs the ITF campaign against FOCs as of ", format(Sys.Date(), '%B %d, %Y'), ". This status may affect the following results, including by increasing apparent consumption of aquatic foods."))
```

```{r create-dataframes, cache=TRUE}
# 1) focal country DWF activities -----------------------
dwf_frgn <- country_i_dwf %>% 
  filter(dwf == "foreign")
  # domestic reference
dwf_dom <- country_i_dwf %>% 
  filter(dwf != "foreign")
  # find most recent 5 years for filtering top species
max_year <- max(dwf_frgn$year)
last_5_yrs_dwf <- seq(max_year - 4, max_year, by = 1)
  # top 6 species caught via dwf
top_6_sp_dwf <- dwf_frgn %>% 
  filter(year %in% c(last_5_yrs_dwf)) %>% 
  group_by(sciname, common_name) %>% 
  summarise(live_weight_t = sum(live_weight_t), # total live weight (tons)
            .groups = "drop") %>% 
  arrange(desc(live_weight_t)) %>% 
  slice_head(n = 6)

# 2) Focal country's consumption -------------------------
  # a) fish caught in its own waters (regardless of who is fishing)
consum_dom <- country_i_consump %>% 
  filter(eez_iso3c == country_iso3c)
  # b) fish caught in different waters: 
    #  - domestic production by a different country (trade)
    #  - dwf production from a different country (trade)
    #  - focal country's dwf catch
consum_frgn <- country_i_consump %>% 
  filter(eez_iso3c != country_iso3c)
  # c) country's consumption of DWF fish
consum_dwf <- country_i_consump %>% 
  filter(dwf == "foreign")
  # find most recent 5 years for filtering top species
max_year <- max(consum_dwf$year)
last_5_yrs_consum <- seq(max_year - 4, max_year, by = 1)
  # top 6 species consumed 
top_6_sp_consum <- consum_dwf %>% 
  filter(year %in% c(last_5_yrs_consum)) %>% 
  group_by(sciname, common_name) %>% 
  # total live_weight
  summarise(live_weight_t = mean(live_weight_t),
            .groups = "drop") %>% 
  arrange(desc(live_weight_t)) %>% 
  slice_head(n = 6)
    
# 3) Fishing activity in focal country EEZ by other countries ---------------
eez_frgn <- country_i_eez_fishing %>% 
  filter(dwf == "foreign")
  # domestic reference - same as dwf_dom
eez_dom <- country_i_eez_fishing %>% 
  filter(dwf != "foreign")
  # find most recent 5 years for filtering top species
max_year <- max(consum_dwf$year)
last_5_yrs_eez <- seq(max_year - 4, max_year, by = 1)
  # top species 
top_6_sp_eez_frgn <- eez_frgn %>% 
  filter(year %in% c(last_5_yrs_eez)) %>% 
  group_by(sciname, common_name) %>% 
  # total live_weight
  summarise(live_weight_t = mean(live_weight_t),
            .groups = "drop") %>% 
  arrange(desc(live_weight_t)) %>% 
  slice_head(n = 6)
```

```{r find-NA-values, eval = FALSE}
# -- For report development only --
# Record missing common_name values for correction in run-analysis-report.R
# add manual correction in the creation of `sciname_common` object.

# DWF species
top_6_csv <- read_csv(file.path("output", "common_name_na.csv"))

na_rows_dwf <- top_6_sp_dwf %>% 
  filter(is.na(common_name))

top_6_csv <- rbind(top_6_csv, na_rows_dwf)

# Consumption species
na_rows_consum <- top_6_sp_consum %>% 
  filter(is.na(common_name))

top_6_csv <- rbind(top_6_csv, na_rows_consum)

# EEZ species
na_rows_eez <- top_6_sp_eez_frgn %>% 
  filter(is.na(common_name))

top_6_csv <- rbind(top_6_csv, na_rows_eez)

write_csv(top_6_csv, file.path("output", "common_name_na.csv"))
```

# Results

## 1) DWF in `r country_name`'s EEZ by other countries

```{r fig-prct-eez-frgn ,fig.cap= glue::glue("percent of catch in {country_name}'s EEZ that is caught by foreign nations.")}
# new figure --
# Time series of percent of catch in Mexico’s EEZ that is caught by foreign nations, possibly as a panel with Fig 20 (fig-line-eez-dwf) below.  

# calc total catch
eez_total_yr <- country_i_eez_fishing %>% 
  group_by(year) %>% 
  summarise(total_catch = sum(live_weight_t))

# calc total foreign eez catch & join to total catch
catch_eez_yr <- eez_frgn %>% 
  group_by(year) %>% 
  summarize(eez_frgn_catch = sum(live_weight_t)) %>% 
  left_join(eez_total_yr, by = "year") %>% 
  mutate(prct_eez_frgn = eez_frgn_catch/total_catch)

# Check if the dataframe is empty
if (nrow(eez_total_yr) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  eez_total_yr <- data.frame(
    year = unique(country_i_eez_fishing$year),
    prct_dwf = 0
  )
}

# Line time series percent of total catch in foreign waters
(fig_eez_prct <- catch_eez_yr %>% 
  ggplot(aes(year,prct_eez_frgn)) +
    geom_line() +
    theme_bw() +
    labs(y = glue("Percent of {country_name}'s EEZ Catch by Foreign Nations"),
         x = "") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                       limits = c(0,1))
)
```

```{r fig-prct-eez-frgn-annote, results='asis'}
```

```{r fig-line-eez-dwf, fig.cap=paste0("The quantity of distant water fishing caught in ", country_name, "'s EEZ by forign countries.")}

eez_frgn_plot <- eez_frgn %>% 
  exploreARTIS::add_country_name("producer_iso3c") %>% 
  exploreARTIS::add_country_name("consumer_iso3c")

# Check if the dataframe is empty
if (nrow(eez_frgn_plot) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  eez_frgn_plot <- data.frame(
    year = unique(country_i_eez_fishing$year),
    producer_iso3c_name = "None",
    live_weight_t = 0  
  )
}

exploreARTIS::plot_ts(eez_frgn_plot,
                      artis_var = "producer_iso3c_name",
                      prop_flow_cutoff = 0.05,
                      plot.type = "stacked",
                      legend.title = "DWF country"
                      ) +
  scale_y_continuous(labels = scales::comma)
  
```

```{r, fig-line-eez-dwf-annote, results='asis'}
```

```{r fig-bar-sp-eez-dwf, eval= nrow(eez_frgn) > 0, fig.cap=paste0("Top species caught in ", country_name, "'s EEZ caught via DWF by foreign countries. Sum of the most recent years of data available (", paste(last_5_yrs_eez, collapse = ", "), ").")}
# Only displays if data is available

exploreARTIS::plot_bar(data = top_6_sp_eez_frgn,
                               bar_group = "common_name",
                               x.lab = "Quantity (tons live weight)") +
  scale_x_continuous(labels = scales::comma) +
  # Add quantity labels for values below the threshold (outside of bar)
  geom_shadowtext(
    data = subset(top_6_sp_eez_frgn, 
                  live_weight_t < max(top_6_sp_eez_frgn$live_weight_t) * 0.8), 
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 0,
    nudge_x = 0.025 * max(top_6_sp_eez_frgn$live_weight_t), # Dynamic nudge value
    colour = "#114F59", # default RGB color from plot_bar
    bg.colour = "white",
    bg.r = 0.2,
    size = 3
  ) +
  # Add quantity labels for values above the threshold (inside bar)
  geom_text(
    data = subset(top_6_sp_eez_frgn, 
                  live_weight_t >= max(top_6_sp_eez_frgn$live_weight_t) * 0.8),
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 1,
    nudge_x = -0.02 * max(top_6_sp_eez_frgn$live_weight_t), # Adjust the nudge value
    colour = "white",
    size = 3
  )
```

```{r fig-bar-sp-eez-dwf-annote, results='asis'}
```

```{r ,eval= nrow(eez_frgn) == 0, results='asis'}
# markdown text only appears if no data
cat(paste0("There is no recorded DWF occuring in ", country_name, " EEZ waters by other countries."))
```

```{r fig-sankey-eez-all, fig.cap= paste0("Flows of all fishing activity occuring in ", country_name,"'s EEZ across all species and years of available data (", paste(unique(country_i_eez_fishing$year), collapse = ", "),").")}
# New Figure --
# Sankey of overall flow (4 columns) with species, EEZ, producer, consumer (or possibly drop species if the 4 columns make it too messy) – focal country will be EEZ in all cases here

eez_fishing_sankey <- country_i_eez_fishing %>%
  exploreARTIS::add_country_name("producer_iso3c") %>%
  exploreARTIS::add_country_name("consumer_iso3c") 

(plot_sankey(eez_fishing_sankey,
             cols = c(
               "common_name",
               "eez_name",
               "producer_iso3c_name",
               "consumer_iso3c_name")) + 
  scale_x_discrete(labels = c("Species", "EEZ", "Producer", "Consumer")) +
  theme(axis.text.x = element_text(size = 8))
)
```

```{r fig-sankey-eez-all-annote, results='asis'}
```

```{r figs-sankeys-eez-frgn-species, results='hide', fig.keep='all', fig.cap=paste0("Total distant water fishing catch in ", country_name, "'s EEZ for ", top_6_sp_eez_frgn$common_name," across all years of available data (", paste(unique(country_i_eez_fishing$year), collapse = ", "),").")}

# New Figure -- 
# Sankey of flows (EEZ, producer, consumer) for top species

eez_frgn_sankey <- eez_frgn %>%
  exploreARTIS::add_country_name("producer_iso3c") %>%
  exploreARTIS::add_country_name("consumer_iso3c") 

purrr::map(top_6_sp_eez_frgn$common_name, 
           ~ plot_sankey(eez_frgn_sankey %>% 
                           filter(.x == common_name),
                         cols = c("eez_name", 
                                  "producer_iso3c_name",
                                  "consumer_iso3c_name"),
                         #prop_flow_cutoff = 0,
                         plot.title = .x) + 
             theme(plot.title = element_text(size=12)) +
             scale_x_discrete(labels = c("EEZ", "Producer", "Consumer")) +
             theme(axis.text.x = element_text(size = 8))
           )
```

```{r fig-sankey-eez-1, results='asis'}
```

```{r fig-sankey-eez-2, results='asis'}
```

```{r fig-sankey-eez-3, results='asis'}
```

```{r fig-sankey-eez-4, results='asis'}
```

```{r fig-sankey-eez-5, results='asis'}
```

```{r fig-sankey-eez-6, results='asis'}
```

## 2) `r country_name` DWF Activities 

```{r fig-prct-dwf, eval= TRUE, fig.cap= paste0("Percent of ", country_name, " total catch that is caught in another country's EEZ via distant water fishing.")}
# calc total catch
catch_total_yr <- country_i_dwf %>% 
  group_by(year) %>% 
  summarise(total_catch = sum(live_weight_t))

# calc total dwf catch & join to total catch
catch_dwf_yr <- dwf_frgn %>% 
  group_by(year) %>% 
  summarize(dwf_catch = sum(live_weight_t)) %>% 
  left_join(catch_total_yr, by = "year") %>% 
  mutate(prct_dwf = dwf_catch/total_catch)

# Check if the dataframe is empty
if (nrow(catch_dwf_yr) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  catch_dwf_yr <- data.frame(
    year = unique(country_i_dwf$year),
    prct_dwf = 0
  )
}

# Line time series percent of total catch in foreign waters
(fig_dwf_prct <- catch_dwf_yr %>% 
  ggplot(aes(year,prct_dwf)) +
    geom_line() +
    theme_bw() +
    labs(y = "Percent Catch in Foreign Waters",
         x = "") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                       limits = c(0,1))
)
```

```{r, 1-fig-prct-dwf, results='asis'}
```

```{r fig-line-dwf-eez, eval= TRUE, fig.cap=paste0("The quantity of distant water fishing caught by ", country_name, " by the source EEZ it was caught and year")}

exploreARTIS::plot_ts(dwf_frgn,
                      artis_var = "eez_name",
                      #plot.title = "DWF Catch by EEZ",
                      prop_flow_cutoff = 0.05,
                      plot.type = "stacked",
                      legend.title = "Source EEZ"
                      ) +
  scale_y_continuous(labels = scales::comma)
```

```{r, fig-line-dwf-eez-annote, results='asis'}
```

```{r fig-bar-dwf-species, eval= nrow(dwf_frgn) > 0, fig.cap=paste0("Top species caught via distant water fishing by tons of live weight. Sum for the most recent available data (", paste(last_5_yrs_dwf, collapse = ", "), ").")}
# Only displays if data is available
exploreARTIS::plot_bar(data = top_6_sp_dwf,
                               bar_group = "common_name",
                               x.lab = "Quantity (tons live weight)") +
  scale_x_continuous(labels = scales::comma) +
  # Add quantity labels for values below the threshold (outside of bar)
  geom_shadowtext(
    data = subset(top_6_sp_dwf, 
                  live_weight_t < max(top_6_sp_dwf$live_weight_t) * 0.8), 
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 0,
    nudge_x = 0.025 * max(top_6_sp_dwf$live_weight_t), # Dynamic nudge value
    colour = "#114F59", # default RGB color from plot_bar
    bg.colour = "white",
    bg.r = 0.2,
    size = 3
  ) +
  # Add quantity labels for values above the threshold (inside bar)
  geom_text(
    data = subset(top_6_sp_dwf, 
                  live_weight_t >= max(top_6_sp_dwf$live_weight_t) * 0.8),
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 1,
    nudge_x = -0.02 * max(top_6_sp_dwf$live_weight_t), # Adjust the nudge value
    colour = "white",
    size = 3
  )
```

```{r, eval = nrow(dwf_frgn) == 0, results='asis'}
cat(paste0("There is no recorded DWF by ", country_name, " in other countries EEZs."))
```

```{r, fig-bar-dwf-species-annote, eval= nrow(dwf_frgn) > 0, results='asis'}
```

```{r fig-sankey-dwf-all, fig.cap= paste0("All flows of ", country_name, "'s distant water fishing activity across species and years of available data (", paste(unique(country_i_eez_fishing$year), collapse = ", "),").")}
# New Figure --
# Sankey of overall flow (4 columns) with species, EEZ, producer, consumer (or possibly drop species if the 4 columns make it too messy) – focal country will be producer in all cases here

dwf_frgn_sankey <- dwf_frgn %>%
  exploreARTIS::add_country_name("producer_iso3c") %>%
  exploreARTIS::add_country_name("consumer_iso3c") 

(plot_sankey(dwf_frgn_sankey,
             cols = c(
               "common_name",
               "eez_name",
               "producer_iso3c_name",
               "consumer_iso3c_name")) + 
  scale_x_discrete(labels = c("Species", "EEZ", "Producer", "Consumer")) +
  theme(axis.text.x = element_text(size = 8))
)
```

```{r fig-sankey-dwf-all-annote, results='asis'}
```

```{r figs-sankeys-dwf-species, results='hide', fig.keep='all', fig.cap=paste0(country_name, "'s total distant water fishing catch of ", top_6_sp_dwf$common_name, " for the most recent available data (", paste(unique(dwf_frgn$year), collapse = ", "), ").")}

# fig.cap = c('first plot', 'second plot') # will provide unique captions to plots
dwf_frgn_sankey <- dwf_frgn %>% 
  exploreARTIS::add_country_name("producer_iso3c") %>% 
  exploreARTIS::add_country_name("consumer_iso3c")

#glimpse(dwf_frgn_consum_sankey)

purrr::map(top_6_sp_dwf$common_name, 
           ~ plot_sankey(dwf_frgn_sankey %>% 
                           filter(.x == common_name),
                         cols = c("eez_name", 
                                  "producer_iso3c_name",
                                  "consumer_iso3c_name"),
                         plot.title = .x) + 
             theme(plot.title = element_text(size=12)) +
             scale_x_discrete(labels = c("EEZ", "Producer", "Consumer")) +
             theme(axis.text.x = element_text(size = 8))
           )
```

```{r, fig-sankey-dwf-1, results='asis'}
```

```{r, fig-sankey-dwf-2, results='asis'}
```

```{r, fig-sankey-dwf-3, results='asis'}
```

```{r, fig-sankey-dwf-4, results='asis'}
```

```{r, fig-sankey-dwf-5, results='asis'}
```

```{r, fig-sankey-dwf-6, results='asis'}
```

## 3) Consumption of DWF by `r country_name`

```{r fig-consump, cache=FALSE, fig.fullwidth=T, out.width="100%", fig.asp=1, fig.width=8.57, fig.cap= paste0(country_name, "'s consumption of catch from its own waters. \"Domestic production\" referes to catch ", country_name, " produces and \"Foreign fleet production\" is a foreign country's catch in ", country_name, "'s water. Note y-axes may not be same scale and years in data may not be consistent.") }

# consum_dom is Focal country consumption of catch in its own waters
# could be domestic catch or catch by a different nation

consum_dom_dom_plot <- consum_dom %>%
  filter(dwf == "domestic",
         producer_iso3c == country_iso3c) %>% 
  mutate(producer_name = countrycode(producer_iso3c,
                                     origin = "iso3c",
                                     destination = "country.name"))

consum_dom_frgn_plot <- consum_dom %>% 
  filter(dwf == "foreign",
         producer_iso3c != country_iso3c) %>% 
  mutate(producer_name = countrycode(producer_iso3c,
                                     origin = "iso3c",
                                     destination = "country.name"))

# Check if the dataframe is empty
if (nrow(consum_dom_frgn_plot) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  consum_dom_frgn_plot <- data.frame(
    year = unique(consum_dom$year),
    producer_name = "None",
    live_weight_t = 0  
  )
}

plot1 <- plot_ts(consum_dom_dom_plot,        
                 artis_var = "producer_name",
                 prop_flow_cutoff = 0.05,
                 plot.type = "stacked",
                 plot.title = "Domestic production"
                 ) +
  scale_y_continuous(labels = scales::comma)

plot2 <- plot_ts(consum_dom_frgn_plot,        
                 artis_var = "producer_name",
                 prop_flow_cutoff = 0.05,
                 plot.type = "stacked",
                 plot.title = "Foreign fleet production"
                 )

egg::ggarrange(plot1, plot2, ncol = 1)
```

```{r, fig-consump-annote, results='asis'}
```

```{r fig-facet-consump, cache=FALSE, fig.fullwidth=T, fig.width=8.57, out.width="100%", fig.cap=paste0("Fish consumed by ", country_name, " from other countries's waters. The left panel is fish caught by ", country_name, " in another country's EEZ and consumed by ", country_name, ". The middle panel is fish caught by another country in its own waters and consumed by ", country_name, " (this scenario is not DWF). The right panel is fish caught by another country in a different country's EEZ that is consumed by ", country_name,".")}
#, out.width="100%",  fig.fullwidth = TRUE, fig.width=8.57,
 # facet line plot - - Other EEZ

# create facet variable for 3 other EEZ consumption scenarios:
 #    domestic production by a different country
 #    dwf production from a different country
 #    focal country dwf
consum_frgn_facet <- consum_frgn %>% 
  mutate(
    consum_foreign = case_when(
      dwf == "domestic" & producer_iso3c != country_iso3c ~ 
        "Foreign country's\n domestic production",
      dwf == "foreign" & producer_iso3c != country_iso3c ~ 
        "Foreign country's\n DWF production",
      dwf == "foreign" & producer_iso3c == country_iso3c ~
        glue("{country_name} DWF\nproduction")),
    producer_name = countrycode::countrycode(producer_iso3c,
                                             origin = "iso3c",
                                             destination = "country.name")
  )

(consum_frgn_facet_plot <- plot_ts(consum_frgn_facet,
                                  artis_var = "producer_name",
                                  plot.type = "stacked",
                                  facet_variable = "consum_foreign",
                                  facet_values = 3,
                                  prop_flow_cutoff = 0.05) +
    scale_y_continuous(labels = scales::comma)
  )

```

```{r, fig-facet-consump-annote, results='asis'}
```

**Note**: `plot_ts()` does not allow vertical stacked facet. When we expand years to all available, This plot will become squished. Can separate into 3 separate plots and `ggarrange()` to stack. Will need flexible calculation to hold y-axes across plots.

```{r, fig-bar-top-sp-consump, eval=TRUE, fig.cap=paste0("Top species consumed by ", country_name, " caught via distant water fishing by ", country_name, " and other countries. Sum of the most recent years of data available (", paste(last_5_yrs_consum, collapse = ", "), ").")}

exploreARTIS::plot_bar(data = top_6_sp_consum,
                               bar_group = "common_name",
                               x.lab = "Quantity (tons live weight)") +
  scale_x_continuous(labels = scales::comma) +
  # Add quantity labels for values below the threshold (outside of bar)
  geom_shadowtext(
    data = subset(top_6_sp_consum, 
                  live_weight_t < max(top_6_sp_consum$live_weight_t) * 0.8), 
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 0,
    nudge_x = 0.025 * max(top_6_sp_consum$live_weight_t), # Dynamic nudge value
    colour = "#114F59", # default RGB color from plot_bar
    bg.colour = "white",
    bg.r = 0.2,
    size = 3
  ) +
  # Add quantity labels for values above the threshold (inside bar)
  geom_text(
    data = subset(top_6_sp_consum, 
                  live_weight_t >= max(top_6_sp_consum$live_weight_t) * 0.8),
    aes(x = live_weight_t, y = common_name, 
        label = scales::comma(round(live_weight_t))),
    hjust = 1,
    nudge_x = -0.02 * max(top_6_sp_consum$live_weight_t), # Adjust the nudge value
    colour = "white",
    size = 3
  )


```

```{r, fig-bar-top-sp-consump-annote, results='asis'}
```

```{r fig-sankey-consump-all, fig.cap= paste0("All flows of ", country_name, "'s distant water fishing consumption across all species and years of available data (", paste(unique(consum_dwf$year), collapse = ", "),").")}
# New Figure
# Sankey of overall flow (4 columns) with species, EEZ, producer, consumer (or possibly drop species if the 4 columns make it too messy) – focal country will be consumer in all cases here

consum_dwf_sankey <- consum_dwf %>%
  exploreARTIS::add_country_name("producer_iso3c") %>%
  exploreARTIS::add_country_name("consumer_iso3c") 

(plot_sankey(consum_dwf_sankey,
             cols = c(
               "common_name",
               "eez_name",
               "producer_iso3c_name",
               "consumer_iso3c_name")) + 
  scale_x_discrete(labels = c("Species", "EEZ", "Producer", "Consumer")) +
  theme(axis.text.x = element_text(size = 8))
)
```

```{r fig-sankey-consump-all-annote, results='asis'}
```

```{r figs-sankey-consump, echo = FALSE, cache = FALSE, results = 'hide', fig.keep = 'all', fig.cap = paste0(country_name, "'s consumption of ", top_6_sp_consum$common_name," caught via distant water fishing for available years of data (", paste(unique(consum_dwf$year), collapse = ", "), "). The flows represent the EEZ where the product was caught, producer country (who caught the product), and consumer country (who consumed the end product).")}

purrr::map(top_6_sp_consum$common_name, 
           ~ plot_sankey(consum_dwf_sankey %>% 
                           filter(.x == common_name),
                         cols = c("eez_name", 
                                  "producer_iso3c_name",
                                  "consumer_iso3c_name"),
                         plot.title = .x) + 
             theme(plot.title = element_text(size=14)) +
             scale_x_discrete(labels = c("EEZ", "Producer", "Consumer")) +
             theme(axis.text.x = element_text(size = 8)) 
           )
```

```{r fig-sankey-consump-1, results='asis'}
```

```{r fig-sankey-consump-2, results='asis'}
```

```{r fig-sankey-consump-3, results='asis'}
```

```{r fig-sankey-consump-4, results='asis'}
```

```{r fig-sankey-consump-5, results='asis'}
```

```{r fig-sankey-consump-6, results='asis'}
```

```{r fig-stacked-consum-dwf,eval=TRUE, fig.cap=paste0("Countries consuming products caught via distant water fishing by ", country_name, " in available years of data (", paste(unique(dwf_frgn$year), collapse = ", "), ").")}

plot_ts(dwf_frgn,
        artis_var = "consumer_iso3c",
        prop_flow_cutoff = 0.05,
        plot.type = "stacked",
        legend.title = "Consumer") +
  scale_y_continuous(labels = scales::comma)
```

```{r, fig-stacked-consum-dwf-annote, results='asis'}
```