---
author: |
  | University of Washington
  | School of Aquatic and Fishery Sciences
  | Seafood Globalization Lab
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
header-includes:
  - \usepackage{placeins}
params: 
  countries_i: NULL
  country_i_dwf: NULL
  country_i_consump: NULL
  country_i_eez_fishing: NULL
---

```{r setup, include=FALSE}

# set global code chunk options
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                     # fig.fullwidth = TRUE,
                      fig.width = 6,
                      fig.asp = 0.618,
                    #  fig.show = "hold",
                    #  fig.pos='ht',
                    #  out.width = "70%",
                    #  fig.align = "center",
                      eval.after = "fig.cap", # eval code first then options
                      cache = TRUE)

# load packages
library(rmarkdown)
library(knitr) # Need package version 1.44 or up for quarto
library(countrycode) # convert and standardize country id
library(magrittr) # pipe function
library(ggplot2) # visualization
library(forcats) #reorder factors
library(stringr)
library(purrr) # iteration 
library(scales) # adjust display of plot numbers
library(cowplot) # arange plots together
# install old version of exploreARTIS
#install_github("Seafood-Globalization-Lab/exploreARTIS@c0f34b90172f716068c9b98df5ed491ca5085162")
# install AM updates branch, force new install, and do not update global enviro package versions
# install_github("Seafood-Globalization-Lab/exploreARTIS@AM-updates",
#                upgrade = "never", 
#                force = TRUE)
library(exploreARTIS) # custom ARTIS viz package 

# load parameter into object
country_iso3c <- params$countries_i

# iso3c to country name
country_name <- countrycode(country_iso3c,
                            origin = "iso3c",
                            destination = "country.name")

# read in annotations script
knitr::read_chunk(file.path(anndir, 
                            glue::glue({country_iso3c},".R")))

# knitr hook to prevent figure floating 
knitr::knit_hooks$set(plot = function(x, options)  {
  paste0(knitr::hook_plot_tex(x, options), "\n\\FloatBarrier\n")
})

```

---
title: |
  | Oceana Distant Water Fishing Report: 
  | `r country_name`
---

# Overview

This report provides an analysis of `r country_name`'s distant water fishing (DWF). 

To alter annotation text for each figure by specific country navigate to `./annotations/` directory and amend individual country `.R` in the respective figure sections. The sections are refereed to in this `.Rmd`'s code chunks with options like this `{r, 1-fig-prct-dwf, results='asis'}`. Please use `markdown` formatting within the `cat()` statement in the annotation files.

There are three aspects of distant water fishing investigated in this report:

1) DWF activities
2) Exports of DWF products
3) Consumption of DWF sourced products

```{r create-dataframes}
# pull out parameters to Rmd environment - contains dwf = foreign and domestic
country_i_dwf <- params$country_i_dwf
country_i_consump <- params$country_i_consump
country_i_eez_fishing <- params$country_i_eez_fishing

# 1) focal country DWF activities
dwf_frgn <- country_i_dwf %>% 
  filter(dwf == "foreign")
  # domestic reference
dwf_dom <- country_i_dwf %>% 
  filter(dwf != "foreign")

# 2) Focal country's consumption 
  # a) fish caught in its own waters (regardless of who is fishing)
consum_dom <- country_i_consump %>% 
  filter(eez_iso3c == country_iso3c)
  # b) fish caught in different waters: 
    #  - domestic production by a different country (trade)
    #  - dwf production from a different country (trade)
    #  - focal country's dwf catch
consum_frgn <- country_i_consump %>% 
  filter(eez_iso3c != country_iso3c)
  # c) country's consumption of DWF fish
consum_dwf <- country_i_consump %>% 
  filter(dwf == "foreign")
    
# 3) Fishing activity in focal country EEZ by other countries
eez_frgn <- country_i_eez_fishing %>% 
  filter(dwf == "foreign")
  # domestic reference - same as dwf_dom
eez_dom <- country_i_eez_fishing %>% 
  filter(dwf != "foreign")
```

# DWF Activities by `r country_name`

```{r eval= TRUE, fig-prct-dwf, fig.cap= paste0("Percent of ", country_name, "total catch that is distant water fishing for most recent available data")}
# calc total catch
catch_total_yr <- country_i_dwf %>% 
  group_by(year) %>% 
  summarise(total_catch = sum(live_weight_t))

# calc total dwf catch & join to total catch
catch_dwf_yr <- dwf_frgn %>% 
  group_by(year) %>% 
  summarize(dwf_catch = sum(live_weight_t)) %>% 
  left_join(catch_total_yr, by = "year") %>% 
  mutate(prct_dwf = dwf_catch/total_catch)

# Check if the dataframe is empty
if (nrow(catch_dwf_yr) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  catch_dwf_yr <- data.frame(
    year = unique(country_i_dwf$year),
    prct_dwf = 0
  )
}

# Line time series percent of total catch in foreign waters
(fig_dwf_prct <- catch_dwf_yr %>% 
  ggplot(aes(year,prct_dwf)) +
    geom_line() +
    theme_bw() +
    labs(y = "Percent Catch in Foreign Waters",
         x = "") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                       limits = c(0,1))
)
```

```{r, 1-fig-prct-dwf, results='asis'}
```

```{r fig-line-dwf-eez, eval= TRUE, fig.cap=paste0("The quantity of distant water fishing caught by ", country_name, " by the EEZ it was caught in and year")}

exploreARTIS::plot_ts(dwf_frgn,
                      artis_var = "eez_name",
                      #plot.title = "DWF Catch by EEZ",
                      prop_flow_cutoff = 0.05,
                      plot.type = "stacked",
                      legend.title = "Source EEZ"
                      ) +
  scale_y_continuous(labels = scales::comma)
```

```{r, 2-fig-line-dwf-eez, results='asis'}
```

Note: Data is filtered to the last 5 years of available data.

```{r fig-bar-dwf-species, eval= nrow(dwf_frgn) > 0, fig.cap=paste0("Top species caught via distant water fishing. Sum for the last 5 years of available data (", paste(unique(dwf_frgn$year), collapse = ", "), ")")}

exploreARTIS::plot_bar(data = dwf_frgn,
                       bar_group = "common_name",
                       x.lab = "Quantity (tons live weight)",
                       top_n = 6) +
  scale_x_continuous(labels = scales::comma)
```

```{r, 3-fig-bar-dwf-species, eval= nrow(dwf_frgn) > 0, results='asis'}
```

```{r}
top_6_sp_dwf <- dwf_frgn %>% 
  group_by(sciname, common_name) %>% 
  summarise(total_live_weight_t = sum(live_weight_t),
            .groups = "drop") %>% 
  arrange(desc(total_live_weight_t)) %>% 
  slice_head(n = 6)
```


```{r fig-stacked-consum-dwf,eval=TRUE, fig.cap=paste0("Distant water fishing exports by ", country_name, " by the end consumer in the most recent years of data (", paste(unique(dwf_frgn$year), collapse = ", "), ") and not including NAs")}

dwf_frgn_consum <- dwf_frgn %>% 
  filter(sciname %in% top_6_sp_dwf$sciname) %>% 
  ungroup()

plot_ts(dwf_frgn_consum,
        artis_var = "consumer_iso3c",
        prop_flow_cutoff = 0.05,
        plot.type = "stacked",
        legend.title = "Consumer") +
  scale_y_continuous(labels = scales::comma)
```

```{r save-top-6-sp-dwf, eval = FALSE}
# Record missing common_name values for correction
top_6_csv <- read_csv(file.path("output", "common_name_na.csv"))

na_rows_dwf <- top_6_sp_dwf %>% 
  filter(is.na(common_name))

top_6_csv <- rbind(top_6_csv, na_rows_dwf)
```


```{r, 4-fig-stacked-consum-dwf, results='asis'}
```

```{r table-dwf-species, eval=FALSE}
knitr::kable(top_6_sp_dwf %>% 
               select(common_name, 
                      sciname, 
                      total_live_weight_t),
            col.names = c("Common name", 
                          "Scientific name", 
                          "live weight (tons)"),
            caption = paste0("Top DWF Species caught by ", country_name, ". Sum of most recent 5 years of data (", paste(unique(dwf_frgn$year), collapse = ", "), ")")
            )
```

```{r, 1-table-dwf-species, results='asis', eval=FALSE}
```

```{r, 5-10-figs-dwf-species-sankeys, eval=FALSE, results='asis'}
```

```{r figs-dwf-species-sankeys,eval=TRUE, echo=FALSE, results='hide', fig.keep='all', fig.pos='h', fig.cap=paste0(top_6_sp_dwf$common_name, ": caught via DWF by ", country_name, " (source EEZ --> producer --> consumer)")}
# fig.cap = c('first plot', 'second plot') # will provide unique captions to plots
dwf_frgn_consum_sankey <- dwf_frgn_consum %>% 
  exploreARTIS::add_country_name("producer_iso3c") %>% 
  exploreARTIS::add_country_name("consumer_iso3c")

glimpse(dwf_frgn_consum_sankey)

purrr::map(top_6_sp_dwf$common_name, 
           ~ plot_sankey(dwf_frgn_consum_sankey %>% 
                           filter(.x == common_name),
                         cols = c("eez_name", 
                                  "producer_iso3c_name",
                                  "consumer_iso3c_name"),
                         plot.title = .x) + 
             theme(plot.title = element_text(size=14)) +
             scale_x_discrete(labels = c("EEZ", "producer", "consumer")) +
             theme(axis.text.x = element_text(size = 8))
           )
```

# Consumption of DWF by `r country_name`

```{r fig-consump,eval=TRUE, out.width="100%", fig.width=8.57,fig.cap= paste0(country_name, " consumption of catch from its own waters. Domestic production referes to catch ", country_name, "produces and Foreign fleet production is a foreign country's catch in ", country_name, " water. Note y-axes may not be same scale.")}

# consum_dom is  Focal country consumption of catch in its own waters
# could be domestic catch or catch by a different nation

consum_dom_dom_plot <- consum_dom %>%
  filter(dwf == "domestic",
         producer_iso3c == country_iso3c) %>% 
  mutate(producer_name = countrycode(producer_iso3c,
                                     origin = "iso3c",
                                     destination = "country.name"))

consum_dom_frgn_plot <- consum_dom %>% 
  filter(dwf == "foreign",
         producer_iso3c != country_iso3c) %>% 
  mutate(producer_name = countrycode(producer_iso3c,
                                     origin = "iso3c",
                                     destination = "country.name"))

# Check if the dataframe is empty
if (nrow(consum_dom_frgn_plot) == 0) {
  # Create a new dataframe with the necessary structure and zero values
  consum_dom_frgn_plot <- data.frame(
    year = unique(consum_dom$year),
    producer_name = "None",
    live_weight_t = 0  
  )
}

plot1 <- plot_ts(consum_dom_dom_plot,        
                 artis_var = "producer_name",
                 prop_flow_cutoff = 0.05,
                 plot.type = "stacked",
                 plot.title = "Domestic production"
                 ) +
  scale_y_continuous(labels = scales::comma)

plot2 <- plot_ts(consum_dom_frgn_plot,        
                 artis_var = "producer_name",
                 prop_flow_cutoff = 0.05,
                 plot.type = "stacked",
                 plot.title = "Foreign fleet production"
                 )
# combine plot side-by-side
cowplot::plot_grid(plot1, plot2)
```

```{r, 11-fig-consump, results='asis'}
```

```{r fig-facet-consump, eval=TRUE, out.width="100%", fig.width=8.57, fig.cap=paste0("Fish consumed by ", country_name, " from other countries's waters. The left panel is fish caught by ", country_name, " in another country's EEZ and consumed by ", country_name, ". The middle panel is fish caught by another country in its own waters and consumed by ", country_name, " (this scenario is not DWF). The right panel is fish caught by another country in a different country's EEZ that is consumed by ", country_name,".")}
#
 # facet line plot - - Other EEZ

# create facet variable for 3 other EEZ consumption scenarios:
 #    domestic production by a different country
 #    dwf production from a different country
 #    focal country dwf
consum_frgn_facet <- consum_frgn %>% 
  mutate(
    consum_foreign = case_when(
      dwf == "domestic" & producer_iso3c != country_iso3c ~ 
        "Foreign country's\n domestic production",
      dwf == "foreign" & producer_iso3c != country_iso3c ~ 
        "Foreign country's\n DWF production",
      dwf == "foreign" & producer_iso3c == country_iso3c ~
        glue("{country_name} DWF\nproduction")),
    producer_name = countrycode::countrycode(producer_iso3c,
                                             origin = "iso3c",
                                             destination = "country.name")
  )

(consum_frgn_facet_plot <- plot_ts(consum_frgn_facet,
                                  artis_var = "producer_name",
                                  plot.type = "stacked",
                                  facet_variable = "consum_foreign",
                                  facet_values = 3,
                                  prop_flow_cutoff = 0.05) +
    scale_y_continuous(labels = scales::comma)
  )

```

```{r, 12-fig-facet-consump, results='asis'}
```

```{r}
# add country names
consum_dwf <- consum_dwf %>% 
  exploreARTIS::add_country_name("producer_iso3c") %>% 
  exploreARTIS::add_country_name("consumer_iso3c")

```

Note: Data is filtered to the last 5 years of available data

```{r, fig-bar-top-sp-consump, eval=TRUE, fig.cap=paste0("Top species consumed by ", country_name, " caught via distant water fishing by ", country_name, " and other countries. Sum of the most recent years of data available (", paste(unique(consum_dwf$year), collapse = ", "), ").")}

exploreARTIS::plot_bar(data = consum_dwf,
                       bar_group = "common_name",
                       x.lab = "Quantity (tons live weight)",
                       top_n = 6) +
  scale_x_continuous(labels = scales::comma)
```

```{r, 13-fig-bar-top-sp-consump, results='asis'}
```

```{r table-top-sp-consumed, eval=FALSE}

top_6_sp_consum <- consum_dwf %>% 
  group_by(sciname, common_name) %>% 
  summarise(total_live_weight_t = mean(live_weight_t),
            .groups = "drop") %>% 
  arrange(desc(total_live_weight_t)) %>% 
  slice_head(n = 6)

knitr::kable(top_6_sp_consum %>% 
               select(common_name, 
                      sciname, 
                      total_live_weight_t),
            col.names = c("Common name", 
                          "Scientific name", 
                          "Mean live weight per year (tons)"),
            caption = paste0("Top species consumed by ", country_name, " caught via DWF by ", country_name, " and other countries. Sum for the last 5 years of data (", paste(unique(consum_dwf$year), collapse = ", "), ")."))
```

```{r, 2-table-top-sp-consumed, results='asis', eval=FALSE}
```

```{r save-top-6-sp-consum, eval=FALSE}
top_6_sp_consum <- consum_dwf %>% 
  group_by(sciname, common_name) %>% 
  summarise(total_live_weight_t = mean(live_weight_t),
            .groups = "drop") %>% 
  arrange(desc(total_live_weight_t)) %>% 
  slice_head(n = 6)

# record missing common name NAs for correction in run-analysis-report.R
top_6_csv <- read_csv(file.path("output", "common_name_na.csv"))

na_rows_consum <- top_6_sp_consum %>% 
  filter(is.na(common_name))

top_6_csv <- rbind(top_6_csv, na_rows_consum)
write_csv(top_6_csv, file.path("output", "common_name_na.csv"))
```

```{r, 14-19-figs-sankey-consump, results='asis'}
```

```{r figs-sankey-consump, eval= TRUE, echo=FALSE, results='hide', fig.keep='all', fig.cap=paste0(top_6_sp_consum$common_name, ": ", country_name, " consumption of distant water fishing products in the most recent available data (", paste(unique(consum_dwf$year), "). The flows represent the EEZ where the product was caught --> producer country (who caught the product) --> consumer country (who consumed the end product))"))}
# eval only if all common names are matched (no NAs)
purrr::map(top_6_sp_consum$common_name, 
           ~ plot_sankey(consum_dwf %>% 
                           filter(.x == common_name),
                         cols = c("eez_name", 
                                  "producer_iso3c_name",
                                  "consumer_iso3c_name"),
                         plot.title = .x) + 
             theme(plot.title = element_text(size=14)) +
             scale_x_discrete(labels = c("EEZ", "Producer", "Consumer")) +
             theme(axis.text.x = element_text(size = 8)) 
           )
```

